The Astropy Project

### 2017-11-23 main.tex
Suggested typos and minor modifications
Further notes:
* Shouldn't one use the traditional "0\farcs 2" rather than "0.2\arcsec"?
* one should uniformize footnote placement, before of after punctuation: "xxx\footnote{yyy}." vs. "xxx.\footnote{yyy}"
* one should uniformize dash length (-- vs. ---) and surroundings (space before or after)
* one should uniformize quotes, `xxx' vs. ``xxx''.

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
general-purpose programming language that is available under a permissive open
source software license free of charge for all major operating systems.
Stable and well-developed packages provide support for array representation and arithmetic
\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{numpy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
by individuals who work on \astropy project in their own personal
time, by individuals or groups to work on \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.
Different funding models have been proposed for support of \astropy in the future
(e.g., \cite{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.},
which, has so far, covered the direct costs incurred by the \astropy project.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes \footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation \footnote{\url{http://docs.astropy.org/en/stable/}}.
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

The \texttt{astropy.constants} subpackage provides a selection of physical and
astronomical constants as \texttt{Quantity} objects (see
\sectionname~\ref{sec:units}).
A brief description of this package was given in \citep{astropy}.
In version 2.0, the built-in constants have been organized into modules for
specific versions of the constant values.
For example, physical constants have \texttt{codata2014} \citep{codata2014} and
\texttt{codata2010} versions.
Astronomical constants are organized into \texttt{iau2015} and \texttt{iau2012}
modules to indicate their sources (resolutions from the International
Astronomical Union, IAU).
The \texttt{codata2014} and \texttt{iau2015} versions are combined into the
default constant value version: \texttt{astropyconst20}.
For compatibility with \astropypkg version 1.3,  \texttt{astropyconst13}
is available and provides access to the adopted versions of the
constants from earlier versions of \astropypkg.
To use previous versions of the constants as \emph{units} (e.g., solar masses),
the values have to be imported directly; with version
2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.

@@

The benchmarks are meant to evolve over time and include an increasing variety of cases. At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks. Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames. For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth. For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, minimum, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools. \tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools. This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages. Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec. These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices? Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity. Is the difference between median and mean significant enough to warrant showing both? A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
\begin{table}
\begin{center}
\begin{tabular}{llcccc}
\hline
\hline
Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
          &           & arcsec & arcsec & arcsec & arcsec \\
\hline
astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
\end{table}

@@

\subsubsection{nddata}

The \package{astropy.nddata} supackage provides three types of functionality: an
abstract interface for representing generic arbitrary-dimensional datasets
intended primarily for subclassing by developers of other packages, concrete
classes building on this interface, and utilities for manipulating these kind of
datasets.

@@

\texttt{Table} objects can now be combined in several different ways. If two
tables have the same rows, we may want to stack them ``vertically'' to create a
new table with the same columns but all rows. If two tables are row-matched but
have distinct columns, we may want to stack them ``horizontally'' to create a
new table with the same rows but all columns. For other situations, more general
table concatenations or joins are also possible when two tables share some
common columns.

@@

\subsection{io}
% Simon

@@

One of the problems when storing a table in an ASCII format is
preserving table meta-data such as comments, keywords and column data
types, units, and descriptions. The newly defined \emph{Enhanced
Character Separated Values} (ECSV,  \citet{ape6}) format makes it
possible to write a table to an ASCII-format file and read it back
with no loss of information. The ECSV format has been designed to be
both human-readable and compatible with most simple CSV readers.

@@

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitides.

@@

The \package{modeling} package now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).

@@

\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   An example of this is given in \figurename~\ref{fig:convolution-example}.  In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.  As of version 2.0, the two methods are consistent and include a suite of consistency checks.

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to NaN in the original data
    (a).  If the data are convolved with a Gaussian kernel on a 9x9 grid using
    scipy's direct convolution (b), any pixel within range of the original NaN
    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
    to zero first: the originally NaN regions are depressed relative to their
    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
    where the missing pixels are replaced with values interpolated from their
    surroundings using the convolution kernel.
    \label{fig:convolution-example}
}
\end{figure}

@@

This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}. This enables significantly more advanced visualizations.

@@

\begin{figure}
\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
\caption{%
An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
\label{fig:wcsaxes}
}
\end{figure}

@@

\package{astropy.visualization} also provides a histogram function, which is a
generalization of \package{matplotlib}’s histogram function, to allow for more
flexible specification of histogram bins.  The function provides several methods
of automatically tuning the histogram bin size. It has a syntax identical to
\package{matplotlib}’s histogram function, with the exception of the \texttt{bins}
parameter, which allows specification of one of four different methods for
automatic bin selection: `blocks', `knuth', `scott', or `freedman'.

>>>>

The development of the \astropypkg core package began as a largely
community-driven effort to standardize core functionality for astronomical
software in \python.
In this way, its genesis differs from but builds upon many substantial and
% * <bsipocz@gmail.com> 2017-11-13T13:13:08.884Z:
%
% how do astroy builds upon these? or it's more like builds upon the developer experience?
%
%
% ^.
former astronomical software development efforts that were commissioned or
initiated through large institutional support, for example IRAF \citep[developed
at NOAO;][]{IRAF}, MIDAS \citep[developed at ESO;][]{MIDAS}, or Starlink
\citep[originally developed by a consortium of UK institutions and now
maintained by the East Asian Observatory;][]{starlink1982,starlink2013}.
More recently, community-driven efforts have seen significant success in the astronomical sciences \citep{yt}.
\python\footnote{\url{https://www.python.org/}} is an increasingly popular,
general-purpose programming language that is available under a permissive open
source software license free of charge for all major operating systems.
Stable and well-developed packages provide support for array representation and arithmetic
\citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}. Tens of thousands of other packages
are available which can help with tasks that are not astronomy specific but
might be performed in the course of astronomical research, for example interfacing with databases or statistical inference.

@@

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
by individuals who work on \astropy project in their own personal
time, by individuals or groups to work on \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.
Different funding models have been proposed for support of \astropy in the future
(e.g., \citealt{2016arXiv161003159M}), but a long-term plan
for sustainability has not yet been established.
The \astropy project has the ability to accept financial contributions
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative,
open source scientific computing.},
which, has so far, covered the direct costs incurred by the \astropy project.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing astronomical
files) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation\footnote{\url{http://docs.astropy.org/en/stable/}}.
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

The \texttt{astropy.constants} subpackage provides a selection of physical and
astronomical constants as \texttt{Quantity} objects (see
\sectionname~\ref{sec:units}).
A brief description of this package was given in \cite{astropy}.
In version 2.0, the built-in constants have been organized into modules for
specific versions of the constant values.
For example, physical constants have \texttt{codata2014} \citep{codata2014} and
\texttt{codata2010} versions.
Astronomical constants are organized into \texttt{iau2015} and \texttt{iau2012}
modules to indicate their sources (resolutions from the International
Astronomical Union, IAU).
The \texttt{codata2014} and \texttt{iau2015} versions are combined into the
default constant value version: \texttt{astropyconst20}.
For compatibility with \astropypkg version 1.3,  \texttt{astropyconst13}
is available and provides access to the adopted versions of the
constants from earlier versions of \astropypkg.
To use previous versions of the constants as \emph{units} (e.g., solar masses),
the values have to be imported directly; with version
2.0, \texttt{astropy.units} uses the \texttt{astropyconst20} versions.

@@

The benchmarks are meant to evolve over time and include an increasing variety of cases. At the moment, the benchmarks are set up as follows - we have generated a standard set of 1000 pairs of random longitudes/latitudes that we use in all benchmarks. Each benchmark is then defined using an input and output coordinate frame, using all combinations of FK4, FK5, Galactic, ICRS and Ecliptic frames. For now we set the epoch of observation to J2000, and the frame to J2000 in the case of the FK5 and ecliptic frames and B1950 for the FK4 frame, but in future we plan to include a larger variety of epochs and equinoxes, as well as tests of conversion to/from Altitude/Azimuth. For each benchmark, we convert the 1000 longitudes/latitudes from the input/output frame with all tools and quantify the comparison by looking at the median, mean, maximum, and standard deviation of the absolute separation of the output coordinates from each pair of tools. \tablename~\ref{tab:coordinate_benchmarks} gives an example of the relative accuracy of the conversion from FK4 to Galactic coordinates for all pairs of tools. This shows for example that \astropy, Kapteyn and PyTPM agree perfectly (to the precision shown), while PALpy, pySLALIB, and PyAST also agree perfectly amongst themselves, but show an offset of around 0.2\arcsec with the former three packages. Finally, PyEphem disagrees with other packages by 0.4--0.8\arcsec. These values are only meant to be illustrative and will change over time as the benchmarks are refined and packages are updated.
%\inlinecomment{Perry G}{Wouldn't the table be better represented as a matrices? Or perhaps as a matrix as a crude image with colors or intensities representing the size of the quantity. Is the difference between median and mean significant enough to warrant showing both? A link to the actual numbers may satisfy readers that want the exact values, but I suspect the majority don't need to see that precision.}
\begin{table}
\begin{center}
\begin{tabular}{llcccc}
\hline
\hline
Package 1 & Package 2 & Median & Mean & Maximum & Std. Dev. \\
          &           & arcsec & arcsec & arcsec & arcsec \\
\hline
astropy  &  kapteyn  & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
kapteyn  &  palpy    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyast    & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pyephem  & 0.459  & 0.458 & 0.860 & 0.231 \\
\nodata  &  pyslalib & 0.218  & 0.196 & 0.249 & 0.056 \\
\nodata  &  pytpm    & 0.000  & 0.000 & 0.000 & 0.000 \\
palpy    &  pyast    & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
pyast    &  pyephem  & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata    &  pyslalib & 0.000  & 0.000 & 0.000 & 0.000 \\
\nodata    &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
pyephem  &  pyslalib & 0.563  & 0.570 & 1.012 & 0.253 \\
\nodata  &  pytpm    & 0.459  & 0.458 & 0.860 & 0.231 \\
pyslalib &  pytpm    & 0.218  & 0.196 & 0.249 & 0.056 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of the accuracy of the FK4 to Galactic transformation between different packages.\label{tab:coordinate_benchmarks}}
\end{table}

@@

\subsubsection{\package{nddata}}

The \package{astropy.nddata} subpackage provides three types of functionality: an
abstract interface for representing generic arbitrary-dimensional datasets
intended primarily for subclassing by developers of other packages, concrete
classes building on this interface, and utilities for manipulating these kind of
datasets.

@@

\texttt{Table} objects can now be combined in several different ways. If two
tables have the same columns, we may want to stack them ``vertically'' to create a
new table with the same columns but all rows. If two tables are row-matched but
have distinct columns, we may want to stack them ``horizontally'' to create a
new table with the same rows but all columns. For other situations, more general
table concatenations or joins are also possible when two tables share some
common columns.

@@

\subsection{\package{io}}
% Simon

@@

One of the problems when storing a table in an ASCII format is
preserving table meta-data such as comments, keywords and column data
types, units, and descriptions. The newly defined \emph{Enhanced
Character Separated Values} (ECSV,  \citealt{ape6}) format makes it
possible to write a table to an ASCII-format file and read it back
with no loss of information. The ECSV format has been designed to be
both human-readable and compatible with most simple CSV readers.

@@

\package{astropy.modeling} provides an efficient way to instantiate the same type of model with many different sets of parameter values by passing the \texttt{n\_models} argument on instantiation, which sets the number of models to instantiate. This creates a model set that can be efficiently evaluated for example, in PSF (point spread function) photometry, all objects in an image will have a PSF of the same functional form, but with different positions and amplitudes.

@@

The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).

@@

The \package{astropy.convolution} subpackage implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   An example of this is given in \figurename~\ref{fig:convolution-example}.  In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.  As of version 2.0, the two methods are consistent and include a suite of consistency checks.

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example.png}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to NaN in the original data
    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
    scipy's direct convolution (b), any pixel within range of the original NaN
    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
    to zero first: the originally NaN regions are depressed relative to their
    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
    where the missing pixels are replaced with values interpolated from their
    surroundings using the convolution kernel.
    \label{fig:convolution-example}
}
\end{figure}

@@

This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas \package{wcsaxes} defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}. This enables significantly more advanced visualizations.

@@

\begin{figure}
\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
\caption{%
An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0~$.0\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
\label{fig:wcsaxes}
}
\end{figure}

@@

\package{astropy.visualization} also provides a histogram function, which is a
generalization of \texttt{matplotlib}’s histogram function, to allow for more
flexible specification of histogram bins.  The function provides several methods
of automatically tuning the histogram bin size. It has a syntax identical to
\texttt{matplotlib}’s histogram function, with the exception of the \texttt{bins}
parameter, which allows specification of one of four different methods for
automatic bin selection: `blocks', `knuth', `scott', or `freedman'.
